Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Edit text to reflect analysis results

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Figure S1, Table S1).

When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (\> 0), 90.61% of being significant (\> 0.05), and 78.94% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (\> 0), 99.42% of being significant (\> 0.05), and 97.73% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).

There was no effect detected for year when predicting the availability of computational methods (code) or data availability (Figures S3, S4; Tables S3, S4).

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Figures S5, S6, Tables S5, S6).

>>>>

There were no clear differences that the analysis could detect between any of the journals as compared with *Phytopathology* for the sharing of computational methods (code); the effects of all parameters were undecided (Figure \@ref(fig:journal-parameters)A, Table S1, Figure S2).

When predicting the availability of data availability as compared with *Phytopathology*, publications in one journal, *Phytopathologia Mediterranea*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Table S2, Figure S3).

The effect of *Phytopathologia Mediterranea* (Median = 1.68, 95% CI [0.78, 2.57]) has a 99.99% probability of being positive (> 0), 99.98% of being significant (> 0.05), and 99.83% of being large (> 0.30). The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19017).

There was no effect detected for year when predicting the availability of computational methods (Table S3, Figure S4).
However, 2018 was clearly different with more data being made available than all other years (Table S4; Figure S5).

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of computational methods (code) or data (Tables S5, S6 and Figures S6, S7).
